Towards an Automated Sportscasting System for Chess

### 2011-05-18 paper/paper.tex
removed the paper(copy) thing

\subsection{Parsing}
We tried various open source PGN parsers, each succumbing to flaws like mishandling uncommon cases (like promotions and special moves like en passant). We based our system on Chesspresso,\footnote{url{http://www.chesspresso.org/}} a Java library for writing chess programs, which we fixed and modified for our needs. Chesspresso takes a PGN file as input and returns a data structure that represents the initial position of the board and the subsequent moves (as well as all metadata necessary to recreate the PGN file). We also extended it to be more robust to variations in input format, in addition to being able to export PGNs in a canonical form, which was crucial for removing duplicates.

\section{Features}
\subsection{Manually Generated Features}
As a first step towards classification, we selected chess-specific manual features from a given position-move pair.  The position-based features involve information such as where the pieces are on the board and potential moves, while the move-based features involve binary information such as if the move is a capturing move or a check.  We list all our hand-selected manual features in Table REF.

\begin{table*}
\begin{tabular}{lp{0.6\textwidth}}
\hline
\textbf{Category} & \textbf{Description} \\ \hline
Position features & Piece location, potential moves per piece, material count, square control. \\
Move features & Capturing move, recapturing move, en passant move, long castling move, short castling move, check move, stalemate move, checkmate move, promotion move.
\end{tabular} 
\caption{List of chess-specific manual features per position.}
\end{table*}

\subsection{Sparse Autoencoding}

>>>>

\subsection{Parsing}
We tried various open source PGN parsers, each succumbing to flaws like mishandling uncommon cases (such as  promotions and special moves like \emph{en passant}). We based our system on Chesspresso,\footnote{url{http://www.chesspresso.org/}} a Java library for writing chess programs, which we fixed and modified for our needs. Chesspresso takes a PGN file as input and returns a data structure that represents the initial position of the board and the subsequent moves (as well as all metadata necessary to recreate the PGN file). We also extended it to be more robust to variations in input format, in addition to being able to export PGNs in a canonical form, which was crucial for removing duplicates.

\subsection{Preparing the Data}
JINGHAO: Write about slicing and tag generation

\section{Features}
\subsection{Sparse auto-encoder}
The sparse auto-encoder is one of many methods in use for unsupervised feature learning~\cite{single-layer-networks-unsupervised-feature-learning}. It takes the form of a feedforward neural network, which consists of an input layer of N nodes, some number of hidden layers, and output layer of M nodes. The value of each layer $\vec{l_i}$ is determined with a weight matrix $W_i$ and a bias vector $b_i$: \[L_i = f(W_i l_{i-1} + b_i),\] where $f(\cdot)$ is a non-linearity like the sigmoid $f(x) = \frac{1}{1 + e^{-z}}$, applied component-wise.

We want to

\subsection{Manually-generated features}
\begin{table*}
\begin{tabular}{lp{0.6\textwidth}}
\hline
\textbf{Category} & \textbf{Description} \\ \hline
Position features & Piece location, potential moves per piece, material count, square control. \\
Move features & Capturing move, recapturing move, en passant move, long castling move, short castling move, check move, stalemate move, checkmate move, promotion move.
\hline
\end{tabular} 
\caption{List of chess-specific manual features per position.}
\end{table*}

As a first step towards classification, we selected chess-specific manual features from a given position-move pair.  The position-based features involve information such as where the pieces are on the board and potential moves, while the move-based features involve binary information such as if the move is a capturing move or a check.  We list all our hand-selected manual features in Table REF.
